%------------------------- Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  \textbf{\Huge \scshape Ernest Lu} \\ \vspace{1pt}
  \small 469-235-0075 $|$ \href{mailto:ernest@berkeley.edu}{\underline{ernest@berkeley.edu}} $|$
  \href{https://www.linkedin.com/in/badint}{\underline{linkedin.com/in/badint}} $|$
  \href{https://github.com/ernest-lu}{\underline{github.com/ernest-lu}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of California, Berkeley}{Berkeley, CA}
{Bachelor of Arts in Computer Science}{Aug. 2021 -- May 2025}
\resumeSubItem
{Relevant Courses: Algorithms (A+), Data Structures (A+),
  Discrete Mathematics (A+), Artificial Intelligence (A), SICP (A+), Databases (A),
  Probability and Random Processes (A), Machine Structures (A), Linear Algebra (A+),
  Quantum Computing (A), Operating Systems (A), Optimization (A+)}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Databricks} {San Francisco, CA}
{Incoming Software Engineering Intern}  {May. 2024 - Aug. 2024}

\resumeSubheading
{The Voleon Group} {Berkeley, CA}
{Software Engineering Intern}  {Jan. 2023 - Apr. 2023; Incoming Spring 2025}
\resumeItemListStart
\resumeItem{Implemented interpolation of impact model computations that sped up portfolio simulations by upwards of 25\%}
\resumeItem{Developed timing tools for plotting, comparing, and aggregating components of simulations}
\resumeItem{Created interfaces and models for functions called millions of times by impact model code}
\resumeItemListEnd

\resumeSubheading
{Roblox}{San Mateo, CA}
{Software Engineering Intern}{May 2022 - Aug. 2022 and May 2023 - Aug. 2023}
\resumeItemListStart
\resumeItem{Fixed production search bugs that prevented results from being shown to daily active users}
\resumeItem{Designed experimentation on search with metrics pipelines and varying search algorithms }
\resumeItem{Developed automatic prioritization system of Jira tickets created from bugs reported by Roblox creators}
\resumeItem{Enabled ticket priority to be updated over time using streaming techniques applied to a delayed queue}
\resumeItem{Worked with Docker, C\#, AWS, Kibana, Airflow, ElasticSearch and Internal Roblox technologies}
\resumeItemListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubheading
{UC Berkeley EECS Department}{Berkeley, CA}
{Academic Intern, Reader, Tutor}{Feb. 2022 - Dec. 2022}
\resumeItemListStart
\resumeItem{Fall 2022 Reader, Spring 2024 Tutor for CS 170: Efficient Algorithms and Intractable Problems}
\resumeItem{Developed full stack project \underline{\href{https://170-leaderboard.vercel.app/}{leaderboard}} utilized by hundreds of teams to check statuses and update solutions}
\resumeItem{Taught in twice-a-week discussion sections for Spring 2022 CS 70: Discrete Mathematics and Probability Theory.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\href{https://github.com/ernest-lu/Fifteem/blob/main/projectreflection.pdf}{\underline{\textbf{Fifteem}}} $|$ \emph{Heuristic Optimization Contest; UC Berkeley Algorithms}}{Apr. 2022 - May 2022}
\resumeItemListStart
\resumeItem{Implemented approximate solution for an NP-Hard problem based on observations of the recursive and greedy structure of the problem.}
\resumeItem{Created executable system that was continuously run overnight to update solution outputs}
\resumeItem{Placed 3rd out of 240 teams that used combinations of computational resources and optimization techniques}
\resumeItemListEnd
\resumeProjectHeading
{\href{https://badimp.vercel.app/}{\underline{\textbf{Badimp}}} $|$ \emph{Algorithms and Data Structures Library}}{Aug. 2022}
\resumeItemListStart
\resumeItem{Created website with copy-pastable implementations of competitive programming algorithms and data structures}
\resumeItem{Wrote and tested algorithms/data structures against extensive list of problems}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Pintos} $|$ \emph{UC Berkeley Operating Systems}}{Sept. 2023 -  Dec. 2023}
\resumeItemListStart
\resumeItem{Implemented functioning operating system with additional threading and file system features}
\resumeItem{Enabled processes to be run with user arguments, create user threads, and traverse file subdirectories}
\resumeItem{Designed implementation details in a group setting, proposing ideas and giving feedback}
\resumeItemListEnd
\resumeSubHeadingListEnd

%----- HONORS ------
\section{Honors}
\resumeSubHeadingListStart
\item{}
\resumeItemListStart
\resumeItem{USACO Platinum Division}
\resumeItem{AIME Qualifier (X2)}
\resumeItem{CodeForces Master Rating (2231)}
\resumeItem{2nd place - UC Berkeley 2023 ACM-ICPC Team Selection Contest}
\resumeItem{ACM-ICPC North American Championship Qualifier – UNT Team 1}
\resumeItemListEnd
\resumeSubHeadingListEnd


%
%-----------Additional Information-----------
\section{Additional Information}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
                \textbf{Languages/Frameworks}{: C++, Python, Java, C, SQL, JavaScript, HTML/CSS, MATLAB, React} \\
                \textbf{Developer Tools}{: Git, Docker, AWS, VS Code, PyCharm, IntelliJ, Eclipse, Vim} \\
          }}
\end{itemize}


%-------------------------------------------
\end{document}

